Type Safe Redis Queries

### 2017-07-12 TyDe2017/sections/Conclusions.tex
Lightweight revisions to reflect some of the reviewers' comment.

By exploiting various recent extensions and type-level programming techniques,
we have designed a domain-specific embedded language \Edis{} which enforces
typing disciplines that keep track of available keys and their types. The
type of a command clearly specifies which keys must or must not present in
the data store, what their types ought to be, as well as how the keys and types are updated after the execution. A program can be constructed only if it does
not throw a runtime type error, and the type also serves as documentation of the
commands. We believe that it is a neat case study of application of type-level programming.

>>>>

By exploiting various recent extensions and type-level programming techniques,
we have designed a domain-specific embedded language \Edis{} which enforces
typing disciplines that keep track of available keys and their types. The
type of a command clearly specifies which keys must or must not present in
the data store, what their types ought to be, as well as how the keys and types are updated after the execution. A program can be constructed only if it does
not throw a runtime type error when it is run with a store whose status matches
its precondition and when it is the sole client interacting with the store.
The type also serves as documentation of the
commands. We believe that it is a neat case study of application of type-level programming.
